---
title: "Geopolitical Events in post-CPA Sudan, 2005 - 2020"
author: "Sri Ramesh"
date: "5/6/2020"
output: html_document
---

```{r setup, include=FALSE}
options(stringsAsFactors = F)
library(leaflet)
library(tidyverse)
```

A quick web map of geopolitical events in Sudan post-2005, which was the year in which the North and South signed the Comprehensive Peace Agreement (CPA). Event data was compiled by the Armed Conflict Location Event Database (ACLED). Circle radius corresponds to the number of fatalities. See the data here: **acleddata.com**

```{r, echo=F}
acled <- read.csv("SL/1900-01-01-2020-05-06-Chile.csv", sep = ";")
#  filter(year > 2005) # Sudan

labs <- lapply(seq(nrow(acled)), function(i) {
  paste0( '<p>', "Source: ", acled[i, "source"], '<p>', 
          "Event Type: ", acled[i, "event_type"], '</p>', 
          "Event Date: ", acled[i, "event_date"], '</p>', 
          "Associated Actor: ", acled[i, "actor1"], '</p>', 
          "Adm 1: ", acled[i, "admin1"], '</p>', 
          "Adm 2: ", acled[i, "admin2"], '</p>', 
          "Location: ", acled[i, "location"], '</p>', 
          "Fatalities: ", acled[i, "fatalities"], '</p>' ) 
})

pal = colorFactor("Dark2", acled$event_type)

acled_map <- acled %>%
  leaflet() %>% addTiles(options = tileOptions(opacity = .6)) %>%
  addCircleMarkers(lng = ~longitude, lat = ~latitude,
                   fillOpacity=1,
                   fillColor = ~pal(event_type),
                   radius=~fatalities*.03,
                   weight=4,
                   stroke=TRUE,
                   label = lapply(labs, htmltools::HTML)) %>%
  addLegend(pal = pal, values = ~event_type, title = "Event Type")

acled_map
```

*The Armed Conflict Location & Event Data Project (ACLED) is a disaggregated data collection, analysis, and crisis mapping project. ACLED is the highest quality and most widely used real-time data and analysis source on political violence and protest around the world. Practitioners, researchers, journalists, and governments depend on ACLED for the latest reliable information on current conflict and disorder patterns. ACLED is a registered non-profit organization with 501(c)(3) status in the United States.*
